---
output:
  md_document:
    variant: markdown_github
---
[![Build Status](https://travis-ci.org/fvafrCU/cleanr.svg?branch=master)](https://travis-ci.org/fvafrCU/cleanr)
[![Coverage Status](https://codecov.io/github/fvafrCU/cleanr/coverage.svg?branch=master)](https://codecov.io/github/fvafrCU/cleanr?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/cleanr)](https://cran.r-project.org/package=cleanr)

# cleanr
Check your R code for some of the most common layout flaws.

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
## Introduction
Please read the vignette. Either [the version on github](http://htmlpreview.github.io/?https://github.com/fvafrCU/cleanr/blob/master/inst/doc/cleanr_Introduction.html)
or the one released on [cran](https://cran.r-project.org/package=cleanr).

Or, after installation, the help page:

```{r, results='asis', echo = FALSE, comment = ""}
print_help <- function(topic, package = NULL) {  
  help_file = utils:::.getHelpFile(help(topic, package = (package)))
  captured <- capture.output(html=tools:::Rd2HTML(help_file))
  captured <- c("<blockquote>", captured, "</blockquote>")
  cat(captured, sep="\n")
  return(invisible(captured))
}
print_help(topic = "cleanr-package", package = "cleanr")
```

## Installation
You can install cleanr from github with:
```{r, eval = TRUE, results = "hide", message = FALSE}
if (! require("devtools")) install.packages("devtools")
devtools::install_github("fvafrCU/cleanr", quiet = TRUE)
```

## cleanr is a fork 
of [coldr](https://github.com/fvafrcu/coldr.git),
which was a set of shell scripts I used to check the file layout (number of 
lines, width of lines and the like) of code files and somehow turned out to be 
an R package.


