---
title: "An Introduction to cleanr"
author: "Andreas Dominik Cullmann"
date: 2016-10-17, 12:44:39
bibliography: biblio.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# 
Coding is an art but most of the code we write is more or less dreadful.
Many tried to teach us how to write code less dreadful, be it implicitly as
@KR did,
be it explicitly as
@cc
did.

If you are concerned about your coding style, you will probably want to lint 
your codes with [lintr]( https://CRAN.R-project.org/package=lintr) or even 
reformat it using [formatR](https://CRAN.R-project.org/package=formatR).

This package tries to help you with your code`s layout:
it checks our code for files too long or wide, functions with too
many lines, too wide lines, too many arguments or nestings too deep.


After loading the package:
```{r, eval = FALSE}
library("cleanr")
```
```{r, echo = FALSE}
library("cleanr")
set_cleanr_options(reset = TRUE)

```

we pick a file we want to check:
```{r}
file_name <- system.file("source", "R", "utils.R", package = "cleanr")

```

```{r}
# dir first
```
# References
